The journey of Multiple Sequence Alignment

### 2021-08-04 MSA_Notum_journey.Rmd
find various domains for WIF proteins add results on tree

names(WIF_hmmscan)[1:25] <- second_line_fields
```

>>>>

names(WIF_hmmscan)[1:25] <- second_line_fields

WIF_hmmscan %>% 
  distinct(target_name, query_name) %>% 
  pivot_wider(names_from = target_name, values_from = target_name,values_fill = "0") %>% 
  unite(col = "domains",2:11) %>% 
  mutate(domains = domains %>% str_remove_all("0_") %>% str_remove_all("_0"),
         query_name = query_name %>% str_replace("\\|","_")) %>% 
  unite(query_name, 1:2, sep = "__DOMAIN__") %>% view()
```
